DRAFT: Week 3: Degree and Centrality

### 2022-03-02 docs/3. SNA - Assignments/sna_Week3/DRAFT-week3-Assignment.Rmd
3.2.22
Can you focus a bit more on just doing the assignment and not trying to be so high speed

@@

    Attribute summary:
  the 10 most common values are:
  JUICE     RUM   SYRUP LIQUEUR BITTERS    SODA   SPICE     GIN  BRANDY   FRUIT 
    135     125     115      84      54      28      19      12       9       7 
```{r STATNET:Path: Length}
library(statnet)

@@

 >head(snEL%e% "ingTyp")

[1] "FRUIT"   "LEAVES"  "JUICE"   "SYRUP"   "LIQUEUR" "RUM"

   >head(snEL %v% "vertex.names")

[1] "(1-INCH-SQUARE) CHUNKS PINEAPPLE" "(1-INCH-SQUARE) PINEAPPLE CHUNKS" "2:1 SIMPLE SYRUP"                
[4] "A WISH FOR GRACE"                 "ABRICOT VIEUX"                    "ABSINTHE BLANC"

>>>>

```{r STATNET: Component Size Distribution}
library(statnet)
library(sna)

component.dist(
  snEL, 
  connected= c("unilateral")) # c("strong","weak","unilateral","recursive"))

component.largest(
  snEL, 
  connected = c("unilateral"), #=c("strong","weak","unilateral" "recursive")
  result = c("graph"), #c("membership", "graph") 
  return.as.edgelist = FALSE)

##### Details: Component Size Distribution 
Components are maximal sets of mutually connected vertices; depending on the definition of “connected” one employs, one can arrive at several types of components. Those supported here are as follows (in increasing order of restrictiveness):

weak: v_1 is connected to v_2 iff there exists a semi-path from v_1 to v_2 (i.e., a path in the weakly symmetrized graph)

unilateral: v_1 is connected to v_2 iff there exists a directed path from v_1 to v_2 or a directed path from v_2 to v_1

strong: v_1 is connected to v_2 iff there exists a directed path from v_1 to v_2 and a directed path from v_2 to v_1

recursive: v_1 is connected to v_2 iff there exists a vertex sequence v_a,...,v_z such that v_1,v_a,...,v_z,v_2 and v_2,v_z,...,v_a,v_1 are directed paths

@@

```{r STATNET:Path: Reachability}
library(statnet)
library(sna)

@@

```{r STATNET:Path: Geodesic number & lengths}
library(statnet)
library(sna)

summary(geodist(snEL, 
        inf.replace=Inf, 
        count.paths=TRUE, # include geodesics 
        predecessors=FALSE,# include predecessor list
        ignore.eval=FALSE, # ignore edge values
        na.omit=FALSE) # remove NA-values edges
        )
```

```{r STATNET:Path: k Path Census}
library(statnet)
library(sna)

summary(kpath.census(snEL, 
             maxlen = 5, 
             mode = "graph",
             tabulate.by.vertex = TRUE, 
             path.comembership = c("none"), # c("none", "sum","bylength"), 
             dyadic.tabulation = c("none") # c("none", "sum", "bylength"))
))
              ##**"sum"* returns a vertex by vertex matrix of source/destination path counts
             ##**"bylength"* disaggregates these counts by path length. 
             ##**"none"* disables this computation.

```
- Aggregate counts of paths/cycles by length (i.e., k).

- Counts of paths/cycles to which each vertex belongs (when tabulate.byvertex==TRUE).

- Counts of path/cycle co-memberships, potentially disaggregated by length (when the appropriate co-membership argument is set to bylength).

- For path.census, counts of the total number of paths from each vertex to each other vertex, possibly disaggregated by length (if dyadic.tabulation=="bylength").

### 2022-03-02 docs/3. SNA - Assignments/sna_Week3/week3_Plots/Scripts_week3_Plots.Rmd
3.2.22
Can you focus a bit more on just doing the assignment and not trying to be so high speed

# IGRAPH
```{r igraph:}

@@

# Plotting: network data

###**Plot Name: smugIG_plot-R_blue-curved-small*
```{r igraph:plot: basic R }

@@

###**Plot: Kamada Kawai **
    ###**Plot Name** igraph_kamadaLayout_smug
```{r igraph: Plot: Kamada Kawai}

@@

###**Plot: Frucherman-Reingold **
   ###**Plot Name** igrap-smugEL_Frucherman-Reingold
```{r igraph:}

@@

# Plotting: attribute data
###**Plot: Color & Attribute**
              ###**Plot Name: $Vertex Naame and $color **

@@

# Statnet
```{r STATNET:}

@@

# Plotting: network data
# Plotting: attribute data

>>>>

# IGRAPH

@@

## Plotting: network data

### Plot Name: smugIG_plot-R_blue-curved-small\*

```{r igraph:plot: basic R }

@@

### **Plot: Kamada Kawai**

**Plot Name** igraph_kamadaLayout_smug

```{r igraph: Plot: Kamada Kawai}

@@

### **Plot: Frucherman-Reingold**

**Plot Name** igrap-smugEL_Frucherman-Reingold

@@

## Plotting: attribute data

### **Plot: Color & Attribute**

**Plot Name: \$Vertex Naame and \$color**

@@

# Statnet

```{r STATNET:}

@@

## Plotting: network data

```{r PLOT: Find strong components}
library(statnet)
library(sna)
cd <- component.dist(
  snEL,
  connected="strong")
cd$membership              #Who's in what component?
cd$csize                   #What are the component sizes?
                           #Plot the size distribution
plot(1:length(cd$cdist),
     cd$cdist/sum(cd$cdist),
     ylim=c(0,1),
     type="h")

lgc<- #Get largest component
  component.largest(snEL,
                    connected="strong")

#Plot g, with component membership
gplot(snEL,
      vertex.col=2+lgc)

#Plot largest component itself 
gplot(component.largest(
  snEL,
  connected="strong",
  result="graph"))

```{r STATNET: PLOT: Find weak components}

library(statnet)
library(sna)
cd<-component.dist(snEL,connected="weak")
cd$membership              #Who's in what component?
cd$csize                   #What are the component sizes?
                           #Plot the size distribution
plot(1:length(cd$cdist),cd$cdist/sum(cd$cdist),ylim=c(0,1),type="h")  
lgc<-component.largest(snEL,connected="weak")  #Get largest component
gplot(snEL,vertex.col=2+lgc)  #Plot g, with component membership
                           #Plot largest component itself 
gplot(component.largest(snEL,connected="weak",result="graph"))
```

```{r}

## Plotting: attribute data

## Plotting:  Path Length and Geodesic Distance

```{r STATNET:Path: Geodesic number & lengths}
library(statnet)
library(sna)

gplot(geodist(snEL, 
        inf.replace=Inf, 
        count.paths=TRUE, 
        predecessors=FALSE,
        ignore.eval=FALSE, 
        na.omit=FALSE)
        )
```
